The Talking Heads Experiment

### 2015-04-27 chap8/chap8.tex
attended to all todonotes

The installation in Antwerp was announced as a ``Laboratory for Cognitive Robotics and Teleportation" \citep{Steels:99b}.
It featured various rooms as shown in the layout in \figref{fig:layout}. The rooms had different functions: 
\begin{enumerate} 
\item The {\itshape central room} which was visible on entering the space contained the experiment itself, i.e. the 
two cameras mounted on tripods, the computers driving them, the screen with geometric figures, and a projection of 
what went on. The activities of the agents were audible through a narration. 
\clearpage
\item A {\itshape reading room} contained background philosophical and scientific 
papers and excerpts from books about language, meaning and their origins. These readings included: \todo{The readings are referred to, but they do not follow after the colon}
\item A {\itshape user interface room} contained a workstation where visitors to the exhibition could create their own 
agents, direct them to play games on certain sites, and teach new words to their agents. 
\end{enumerate}

\begin{figure}[bp]
  \centerline{\frame{\includegraphics[width=0.9\textwidth]{chap8/figures/layout.pdf}}}
\caption{\label{fig:layout}Layout of the ``Laboratory for Cognitive Robotics and Teleportation" at the Laboratorium exhibition in Antwerp.}
\end{figure}

@@

A typical example of the kind of images that the cameras picked up are shown in \figref{fig:images}. 
To play a game, the agent had to find a sufficiently delineated group of objects and each object had \todo{I have framed Figure 8.2 because it contains multiple images}
to exceed a minimal size. Initially quite complex configurations were put on the white board but this made it very difficult for agents to find a coherent group and to develop good concepts for referring to the topic. The right 
image in \figref{fig:images} provides clear examples of up, down, left and right, different colors, and 
also opportunities to use multiple words (such as `red bottom').

@@

I'm off home now. If you need me to come back and kick 
the server, call me on:
	+33-1-42-78-73-88 \todo{If this was a private number, we would not show it here.}
Bye,
	A
\end{mail}

@@

By mid July,\todo{removed `both' here} the basic infrastructure, the teleportation mechanisms and the semiotic dynamics were running 
smoothly and so the experiment could operate without constant care.

@@

The field of complex systems science was at that time still in its infancy and 
adequate tools for analysing language as a complex adaptive system were in the early stages of development. 
Nevertheles, various publications were \todo{Here the rest of the sentence seems to have disappeared.}

>>>>

The installation in Antwerp was announced as a ``Laboratory for Cognitive Robotics and Teleportation" \citep{Steels:99b}.
It featured various rooms as shown in the layout in \figref{fig:layout}. The rooms had different functions: 
\begin{enumerate} 
\item The {\itshape central room} which was visible on entering the space contained the experiment itself, i.e. the 
two cameras mounted on tripods, the computers driving them, the screen with geometric figures, and a projection of 
what went on. The activities of the agents were audible through a narration. 
\clearpage
\item A {\itshape reading room} contained background philosophical and scientific 
papers and excerpts from books about language, meaning and their origins. 
\item A {\itshape user interface room} contained a workstation where visitors to the exhibition could create their own 
agents, direct them to play games on certain sites, and teach new words to their agents. 
\end{enumerate}

\begin{figure}[bp]
  \centerline{\includegraphics[width=0.9\textwidth]{chap8/figures/layout.pdf}}
\caption{\label{fig:layout}Layout of the ``Laboratory for Cognitive Robotics and Teleportation" at the Laboratorium exhibition in Antwerp.}
\end{figure}

@@

A typical example of the kind of images that the cameras picked up are shown in \figref{fig:images}. 
To play a game, the agent had to find a sufficiently delineated group of objects and each object had 
to exceed a minimal size. Initially quite complex configurations were put on the white board but this made it very difficult for agents to find a coherent group and to develop good concepts for referring to the topic. The right 
image in \figref{fig:images} provides clear examples of up, down, left and right, different colors, and 
also opportunities to use multiple words (such as `red bottom').

@@

I'm off home now. If you need me to come back and kick 
the server, call me on:
	+33-1-42-78-xx-xx 
Bye,
	A
\end{mail}

@@

By mid July, the basic infrastructure, the teleportation mechanisms and the semiotic dynamics were running 
smoothly and so the experiment could operate without constant care.

@@

The field of complex systems science was at that time still in its infancy and 
adequate tools for analysing language as a complex adaptive system were in the early stages of development.
